Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-25 Scripts/Initial_Analysis.Rmd
Fixed results paths for hall 1000

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
  DBEM_path <- paste(data_path,"DBEM/",sep="")
  result_path <- paste(here(),"/Temporal_Data/Results/",sep="")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
  DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
  result_path <- paste(here(),"/Results/",sep="")
}

>>>>

# Set paths depending on machine Beast (jepa88), "carmelia" or Hall1000
if(Sys.info()[7] == "jepa88"){
  data_path <- "Z:/DATA/DBEM/"
}
if(Sys.info()[7] == "carmelia"){
  data_path <- paste(here(),"/Temporal_Data/",sep = "")
  DBEM_path <- paste(data_path,"DBEM/",sep="")
  result_path <- paste(here(),"/Temporal_Data/Results/",sep="")
}
if(Sys.info()[7] == "hall1000"){
  data_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Data/"
  DBEM_path <- "/Volumes/DATA/DATA/DBEM/"
  result_path <- "/Volumes/DATA/JULIANO_NEYMAR/TransEmergence/Results/"
}
